04_validation

### 2022-07-18 replication_data/rmd/01_compile_saves_and_align.Rmd
v1.1 first self contained hopefully

#Only a project lead can run this code. Copy (NEVER MOVE) the original save files to the data_temp folder. And then verify that that data_temp is on the gitignore list so it never gets committed.
path <- paste0(here::here(), "/replication_data/ignore/icb_worker_saves") #this folder is copied over from the dropbox folder and never committed to github
files_worker_saves <- list.files(path = path, pattern = ".Rdata", all.files = FALSE, full.names = T, recursive = T, ignore.case = FALSE, include.dirs = FALSE)
length(files_worker_saves) #32748

>>>>

#Only a project lead can run this code. Copy (NEVER MOVE) the original save files to the data_temp folder. And then verify that that data_temp is on the gitignore list so it never gets committed.
path <- paste0(here::here(), "/git_ignore_folder/icb_worker_saves") #this folder is copied over from the dropbox folder and never committed to github
files_worker_saves <- list.files(path = path, pattern = ".Rdata", all.files = FALSE, full.names = T, recursive = T, ignore.case = FALSE, include.dirs = FALSE)
length(files_worker_saves) #32748

### 2022-07-18 replication_data/rmd/03_aggregation.Rmd
v1.1 first self contained hopefully

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds")) %>%
                  filter(!varname %in% c("lastviewed","crisis",'sentencenumber','crisno', 'icb_survey_version',  'section' )) %>%
                  select(-sentence, -sentence_clean, -varname, -value, -status) %>% 
                  distinct()
dim(icb_long_clean)  
#icb_long_clean %>% count(varname_normalized) %>% arrange(desc(n)) %>% View()

@@

saveRDS(votes_per_crisis_sentence, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.Rds")) 
readr::write_tsv(votes_per_crisis_sentence, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.tsv"))

saveRDS(icb_long_clean, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long.Rds")) 
readr::write_tsv(icb_long_clean, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long.tsv"))

saveRDS(icb_events, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.Rds")) 
readr::write_tsv(icb_events, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.tsv"))

saveRDS(icb_events_long, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.Rds")) 
readr::write_tsv(icb_events_long, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.tsv"))

>>>>

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_clean.Rds")) %>%
                  filter(!varname %in% c("lastviewed","crisis",'sentencenumber','crisno', 'icb_survey_version',  'section' )) %>%
                  select(-sentence, -sentence_clean, -varname, -value, -status) %>% 
                  distinct()
dim(icb_long_clean)  
#icb_long_clean %>% count(varname_normalized) %>% arrange(desc(n)) %>% View()

@@

saveRDS(votes_per_crisis_sentence, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.Rds")) 
#readr::write_tsv(votes_per_crisis_sentence, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_agreement.tsv"))

saveRDS(icb_long_clean, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long.Rds")) 
#readr::write_tsv(icb_long_clean, paste0(here::here(), "/replication_data/out/ICBe_V1.1_long.tsv"))

saveRDS(icb_events, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.Rds")) 
#readr::write_tsv(icb_events, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed.tsv"))

saveRDS(icb_events_long, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.Rds")) 
#readr::write_tsv(icb_events_long, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_long.tsv"))

### 2022-07-18 replication_data/rmd/04_validation.Rmd
v1.1 first self contained hopefully

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/ICBe_V1.1_long_clean.Rds")) %>%
                  filter(!varname %in% c("lastviewed","crisis",'sentencenumber','crisno', 'icb_survey_version',  'section' )) %>%
                  select(-sentence, -sentence_clean, -varname, -value, -status) %>% 
                  distinct()

@@

saveRDS(ICBe_events_agreed_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds")) 
readr::write_tsv(ICBe_events_agreed_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.tsv"))

saveRDS(ICBe_crises_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_crises_markdown.Rds")) 
readr::write_tsv(ICBe_crises_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_crises_markdown.tsv"))

>>>>

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/out/ICBe_V1.1_long_clean.Rds")) %>%
                  filter(!varname %in% c("lastviewed","crisis",'sentencenumber','crisno', 'icb_survey_version',  'section' )) %>%
                  select(-sentence, -sentence_clean, -varname, -value, -status) %>% 
                  distinct()

@@

saveRDS(ICBe_events_agreed_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.Rds")) 
#readr::write_tsv(ICBe_events_agreed_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_events_agreed_markdown.tsv"))

saveRDS(ICBe_crises_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_crises_markdown.Rds")) 
#readr::write_tsv(ICBe_crises_markdown, paste0(here::here(), "/replication_data/out/ICBe_V1.1_crises_markdown.tsv"))
